\documentclass[11pt]{article}
\usepackage{nopageno}
\setcounter{secnumdepth}{1}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\titleformat{\section}[runin]{\normalfont\bfseries}{\thesection}{1em}{}[]
\titlespacing*{\section}{0pt}{0.1\baselineskip}{1ex}
\titleformat{\subsection}[runin]{\normalfont\bfseries}{\thesubsection}{1em}{}[:]
\titlespacing*{\subsection}{0pt}{0.1\baselineskip}{1ex}
\usepackage{enumitem}
\begin{document}
\pagestyle{empty}

\noindent \textbf{Data Management and Sharing Plan}
\vspace{0.3cm}

\section{Roles and Responsibilities}
% QUESTION: Which PI is the data management lead?
%   Recommend Napolitano (Penn State) as lead given existing DesignSafe affiliation
%   and ICDS-ACI storage infrastructure from the prior grant.
%   Wauthier and Busse are secondary data custodians for their respective data streams.
The Principal Investigator (PI), Dr.\ Rebecca Napolitano (Penn State), will have
primary responsibility for data management throughout the project lifecycle and will
ensure data is collected, stored, preserved, and shared in accordance with this plan
and NSF policies.
Co-PI \textbf{Wauthier} (\placeholder{Institution}) is responsible for SAR data
products and coherence time series.
Co-PI \textbf{Busse} (\placeholder{Institution}) is responsible for hydrological
model inputs, outputs, and associated metadata.

\vspace{0.3cm}
\section{Expected Data and Formats}
This project will generate the following data types:

\begin{itemize}
\item[] \textbf{SAR coherence time series (Sentinel-1, Capella):}
  Interferometric coherence and amplitude stacks for Montpelier, VT and Marshall, NC.
  Formats: GeoTIFF (.tif), NetCDF (.nc), CSV summary tables (.csv).
  % QUESTION (Wauthier): Confirm formats.  Are processed products stored as
  %   GeoTIFFs (SNAP/ISCE output), NetCDF stacks (MintPy), or both?
\item[] \textbf{Hydrological mass balance model outputs:}
  Drainage timescale estimates, watershed routing outputs, uncertainty envelopes.
  Formats: NetCDF (.nc), CSV (.csv).
  % QUESTION (Busse): Confirm formats and model software.
\item[] \textbf{Bayesian posterior distributions:}
  Posterior duration distributions per building or spatial unit, credible intervals.
  Formats: Python pickle (.pkl), NetCDF (.nc), CSV summary tables.
  % QUESTION: Will the Bayesian code be on GitHub?  Confirm open-source license.
  %   Recommended: MIT license.
\item[] \textbf{Fragility surface parameters:}
  Duration-damage fragility surfaces for pre-code load-bearing archetype(s).
  Formats: CSV (.csv), MATLAB (.mat) or Python (.pkl).
\item[] \textbf{Community co-design workshop materials:}
  Workshop notes, participant feedback, facilitation guides.
  Formats: PDF (.pdf), anonymized transcripts (.txt, .docx).
  % NOTE: Workshop materials involving human subjects will be anonymized
  %   before sharing.  See Ethics and Privacy section.
\item[] \textbf{Decision framework outputs:}
  Building-specific retrofit recommendations and what-if simulation outputs.
  Formats: CSV (.csv), PDF reports for community partners.
\item[] \textbf{Dissemination materials:}
  Publications, presentations, webinars (.pdf, .pptx, .mp4).
\end{itemize}

Metadata will include instrument specifications (SAR sensor, orbit, acquisition dates),
data processing parameters (coherence window, multi-look factors), and model version
information.

\vspace{0.3cm}
\section{Access, Sharing, and Reuse Policies}
SAR coherence products, mass balance outputs, posterior distributions, and fragility
surface parameters will be shared via DesignSafe-CI under open-access licenses upon
publication or within 12 months of data collection completion.
Bayesian fusion and decision framework code will be released on GitHub under an
open-source license (\placeholder{confirm: MIT or Apache 2.0}).
% QUESTION: Confirm open-source license for code release.
Community workshop materials will be anonymized; access to identifiable materials
will be restricted to project personnel.
Publications and presentations will be made openly available via institutional
repositories.

The hazard-related data and metadata will be archived on the Data Depot at
DesignSafe-CI (the standard repository for the natural hazards community), following
established standards listed on the DesignSafe-CI website and subject to
DesignSafe-CI Data Sharing and Archiving Policies.

\section{Reproducibility}
All data processing and analysis scripts will be version-controlled using Git and
stored on GitHub with appropriate documentation.
Computational environments will be documented using Docker containers or Conda
environment files, with configuration files shared alongside data.
All statistical analyses and visualizations will include code to reproduce them from
processed data.
Open-source software tools will be prioritized to remove licensing barriers.

\section{Data Storage, Preservation and Backup}
All data and code will be archived on DesignSafe-CI.
PI Napolitano is an affiliate of Penn State's Institute for Computation and Data
Science (ICDS) and, through its Advanced Cyber Infrastructure (ICDS-ACI), has access
to active and near-line storage that is backed up daily.
Co-PIs Wauthier and Busse will maintain local backups at their institutions during
active research phases, with regular synchronization to the shared DesignSafe-CI
project workspace.

\vspace{0.3cm}
\section{Ethics and Privacy}
The project will comply with all relevant regulations, including Institutional Review
Board (IRB) requirements for human subjects research.
Community co-design workshop participants will be fully informed of data collection
and sharing plans.
Workshop notes will be anonymized before sharing; personally identifiable information
will be protected using encryption and access controls.
% QUESTION: Does PI Napolitano have existing IRB coverage for community engagement
%   that can be extended, or will a new protocol be needed?
%   The prior grant had IRB approval for Marshall community conversations —
%   confirm with Penn State IRB whether an amendment or new submission is required.
This plan will be reviewed annually and revised as needed in consultation with the
Penn State IRB.

\end{document}
