\documentclass[11pt]{article}
\usepackage{nopageno}
\setcounter{secnumdepth}{1}
\usepackage[margin=1in]{geometry}
\begin{document}
\pagestyle{empty}

\noindent \textbf{Mentoring Plan:}

% QUESTION: How many graduate students total, and who advises each?
%   Suggested: 1 PhD student advised by Napolitano (structural/community);
%   1 PhD student or postdoc advised by Wauthier (SAR); 1 PhD student or
%   postdoc advised by Busse (hydrology).  Cross-advising is strongly recommended
%   for a CPS grant — at minimum, one co-advised student.
% QUESTION: Are there postdocs on any of the three groups?
% QUESTION: What are Wauthier's and Busse's institutions?

\noindent The project will involve:
a PhD student advised by PI Napolitano (Penn State) and co-mentored by co-PIs
Wauthier and Busse through their committee;
\placeholder{describe Wauthier's advisee: PhD student or postdoc, institution,
  primary research focus (SAR processing, coherence analysis)};
\placeholder{describe Busse's advisee: PhD student or postdoc, institution,
  primary research focus (hydrological modeling, uncertainty quantification)}.
The mentoring plan will be updated annually based on the feedback and needs of the
mentees.
The success of the mentoring plan will be assessed through regular progress reports,
participant feedback, and participants' academic and professional achievements.
By providing mentoring and support, the project aims to develop well-rounded,
competent, and confident researchers prepared to address complex challenges at the
intersection of SAR remote sensing, probabilistic structural modeling, community
resilience, and data science.

Mentoring activities will include but not be limited to:

\noindent \textbf{Regular one-on-one meetings:}
PI Napolitano will hold weekly meetings with her advisee to discuss research progress,
challenges, and opportunities.
Co-PIs Wauthier and Busse will do the same with their respective advisees.
All three PIs will hold monthly cross-team meetings to facilitate cross-disciplinary
mentoring and coordination.

\noindent \textbf{Cross-disciplinary co-mentoring:}
Each graduate student will participate in at least one extended visit (1–2 weeks) to
a co-PI's research group per year, allowing direct engagement with the methods and
data streams outside their primary specialization.
PI Napolitano's student will spend time with Wauthier's group to develop SAR
processing fluency; Wauthier's and Busse's advisees will attend Napolitano's annual
community co-design workshops to gain exposure to participatory research methods.
% QUESTION: Is a more formal student exchange (e.g., semester co-residency) feasible
%   given the three institutions involved?  This would be a notable strength.

\noindent \textbf{Career counseling and professional development:}
Mentees will be encouraged to present at conferences (e.g., AGU, ASCE Engineering
Mechanics Institute, Association for Preservation Technology) and submit papers to
peer-reviewed journals.
Each PI will provide career counseling on academic, industry, and government career
pathways relevant to the mentee's disciplinary background.

\noindent \textbf{Training in grant proposal and scholarly communication:}
Mentees will receive training and guidance on preparing NSF grant proposals,
peer-reviewed publications, and conference presentations.
PI Napolitano will make available materials from her graduate-level research methods
course.
\placeholder{Describe equivalent writing/communication training resources at
  Wauthier's and Busse's institutions.}
% QUESTION: Do Wauthier's and Busse's institutions have Graduate Writing Centers
%   or equivalent programs?

\noindent \textbf{Teaching and mentoring skill development:}
Mentees will have opportunities to assist in developing and delivering course content
related to the project.
PI Napolitano will provide guidance on effective teaching techniques and, as
applicable, encourage mentees to pursue the Penn State Center for the Integration of
Research, Teaching and Learning Certificate.
Mentees will also receive mentorship on supervising undergraduate students through
the PSU Undergraduate Research and Fellowships Mentoring program.

\noindent \textbf{Undergraduate research involvement:}
Undergraduate students hired for this project will participate in the Building
Engineering Seminal Undergraduate Research Experience (BESURE) program at Penn State,
providing support through the Women in Science and Engineering Research (WISER) and
Minority Undergraduate Research Experience (MURE) programs.
\placeholder{Describe equivalent undergraduate research programs at Wauthier's and
  Busse's institutions that will be leveraged for this project.}
% QUESTION (Wauthier, Busse): Do your institutions have equivalent undergraduate
%   research programs that should be mentioned here?

\noindent \textbf{Collaboration and diversity training:}
Mentees will be encouraged to collaborate with researchers from diverse backgrounds
and disciplinary areas.
All mentees will participate in diversity, equity, and inclusion training, including
programming offered at their respective institutions on unconscious bias and workplace
inclusion.

\noindent \textbf{Responsible professional practices:}
All mentees will receive training in responsible conduct of research, including
research ethics, data management, and intellectual property rights, through their
institutions' research integrity education programs.
Each PI will also discuss professional practices including time management,
work-life balance, and professional etiquette.

\end{document}
