\documentclass[11pt]{article}
\usepackage{nopageno}
\setcounter{secnumdepth}{1}
\usepackage[margin=1in]{geometry}
\begin{document}

\pagestyle{empty}

% Project Summary — 1 page maximum (NSF PAPPG requirement).
% Must contain three labeled subsections: Overview, Intellectual Merit,
% and Broader Impacts.  Must not contain URLs or hyperlinks.
% All three PIs must be named.

\vspace{-0.3cm}
\subsection{Overview}
\vspace{-0.3cm}
PIs Napolitano (Penn State, structural vulnerability and community co-design),
Wauthier (\placeholder{Institution}, SAR processing and uncertainty quantification),
and Busse (\placeholder{Institution}, hydrological modeling and mass balance)
propose a closed-loop cyber-physical system (CPS) for flood duration estimation,
pre-code building vulnerability assessment, and community retrofit decision support
in small riverine communities.
% QUESTION: Confirm institution names for Wauthier and Busse.
The small, aging communities most repeatedly devastated by riverine flooding are the
least equipped to use existing flood damage assessment frameworks, which require
hydrodynamic simulation pipelines demanding data, software, and expertise far beyond
what small municipalities can sustain.
Our community partners in Montpelier, VT and Marshall, NC have specifically identified
inundation \textit{duration}—not just peak flood stage—as the decision-relevant
variable motivating every modeling constraint in this proposal.

The proposed system has four coupled layers.
The \textbf{physical layer} is the flood-building interaction system: pre-code
load-bearing masonry and timber structures ubiquitous across small historic riverine
communities yet absent from every existing vulnerability framework.
The \textbf{sensing layer} is multi-temporal Sentinel-1 C-band and Capella X-band
SAR coherence and amplitude time series that track the physical state of flooded
building surfaces through the recovery period.
The \textbf{cyber layer} is a Bayesian data fusion framework integrating SAR coherence
persistence with community-scale hydrological mass balance into probabilistic
inundation duration estimates with propagated uncertainty.
The \textbf{decision layer} is a retrofit allocation framework, co-designed with
community stakeholders, that maps probabilistic duration outputs to building-specific
damage state probabilities and actionable retrofit guidance.
The closed loop—satellite sensing to probabilistic inference to community decision to
physical change, validated by post-retrofit SAR acquisitions—is the defining CPS
contribution of this work.

\vspace{-0.5cm}
\subsection{Intellectual Merit}
\vspace{-0.3cm}
The intellectual merit of this research rests on two contributions.
First, we establish that community-accessible sensing modalities, fused under a
Bayesian probabilistic machine learning architecture, can substitute for
resource-intensive physics-based simulation intermediaries in closed-loop CPS
decision systems—a generalizable principle for infrastructure contexts that cannot
support full hydrodynamic modeling.
Second, we advance a community co-design methodology that treats locally held
knowledge as structural input to model validation, contributing to CPS practice for
socio-technical systems where stakeholder knowledge cannot be separated from system
calibration.
Two independent flood events—Montpelier 2023 and Marshall 2024—provide model
validation across heterogeneous community contexts; the contrast isolates which
framework components transfer across contexts and which require local calibration,
establishing the scientific basis for generalization.
Preliminary Sentinel-1 coherence analysis of Montpelier 2023 across four
polarization/orbit combinations shows consistent coherence depression concentrated
in the downtown core persisting nearly two weeks post-peak, establishing the
observational foundation for the proposed framework.

\vspace{-0.5cm}
\subsection{Broader Impacts}
\vspace{-0.3cm}
The closed-loop CPS framework transforms how flood-affected communities interact
with infrastructure sensing, enabling duration-based damage assessment where no
path currently exists.
The decision layer and co-design process are designed for communities without ongoing
research support.
Graduate students will receive cross-disciplinary training in SAR remote sensing,
probabilistic structural modeling, and participatory community research.
The CIR co-design methodology, documented as a transferable protocol, advances CPS
practice for connected communities, establishing how resident knowledge anchors
model validation and community decisions feed back into physical infrastructure
sensing across networks of similarly situated towns.
The framework is designed for open-source release, enabling communities beyond
Montpelier and Marshall to apply duration-based damage assessment using freely
available Sentinel-1 data.

\end{document}
